Lonely and online: an investigation of social media use and social isolation in China

### 2024-06-10 tandf/Social-Isolation-in-China-jg-revised.tex
Compiled mac version

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Lonely and online: an investigation of social media use and social isolation in China},
  pdfkeywords={Social Isolation, Social Media, Digital
Communication, China},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keywords}
    Social Isolation, Social Media, Digital Communication, 
    China
\end{keywords}
\newpage{}

\section{Introduction}\label{introduction}

@@

\section{Literature Review and
Theory}\label{literature-review-and-theory}

@@

\section{Data, Measurement, and
Descriptives}\label{data-measurement-and-descriptives}

@@

\centering{

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-social-iso-dist-1.pdf}

@@

\end{figure}%

@@

\centering{

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-var-dist-1.pdf}

@@

\centering{

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-sm-use-dist-1.pdf}

@@

\centering{

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-urban-dist-1.pdf}

@@

\section{Results}\label{results}

@@

\begin{table}

\caption{\label{tbl-profile-models}Modeling Profiles of Digital
Communication}

\centering{

\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
  & Human Interaction & Online/Offline Interaction & General Social Media\\
\midrule
SES & \num{2.35}* & \num{2.16}* & \num{0.24}*\\
 & (\num{0.27}) & (\num{0.28}) & (\num{0.03})\\
Female & \num{-0.03} & \num{-0.35}* & \num{0.01}\\
 & (\num{0.08}) & (\num{0.08}) & (\num{0.01})\\
CCP Member & \num{-0.17} & \num{0.23}* & \num{0.01}\\
 & (\num{0.09}) & (\num{0.09}) & (\num{0.01})\\
Age & \num{0.51}* & \num{-0.82}* & \num{-0.12}*\\
 & (\num{0.26}) & (\num{0.27}) & (\num{0.02})\\
\midrule
N & \num{2277} & \num{2276} & \num{2198}\\
Pseudo R2 & \num{0.07} & \num{0.05} & \\
R2 &  &  & \num{0.05}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.05}\\
\end{tabular}
\begin{tablenotes}
\item \textit{Note: } 
\item Human Interaction and Offline/Online Relationships estimates are derived from ordered logit and General Social Media from ordinary least squares.
\end{tablenotes}
\end{threeparttable}

\end{table}%

@@

\begin{table}

\caption{\label{tbl-social-isolation-models}Modeling Social Isolation}

\centering{

\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
Human Interaction & \num{-0.14}* & \num{-0.04} & \num{-0.14}* & \num{-0.14}*\\
 & (\num{0.02}) & (\num{0.04}) & (\num{0.02}) & (\num{0.02})\\
Online-Offline & \num{0.07}* & \num{0.07}* & \num{0.15}* & \num{0.07}*\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.03}) & (\num{0.01})\\
Social Media & \num{0.05}* & \num{0.05}* & \num{0.05}* & \num{0.13}*\\
 & (\num{0.03}) & (\num{0.02}) & (\num{0.02}) & (\num{0.05})\\
Urbanicity & \num{-0.04}* & \num{0.02} & \num{0.01} & \num{0.04}\\
 & (\num{0.01}) & (\num{0.03}) & (\num{0.02}) & (\num{0.05})\\
SES & \num{-0.04} & \num{-0.04} & \num{-0.04} & \num{-0.04}\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & \vphantom{1} (\num{0.03})\\
Female & \num{0.02}* & \num{0.02}* & \num{0.02}* & \num{0.02}*\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & \vphantom{1} (\num{0.01})\\
CCP Member & \num{0.00} & \num{0.00} & \num{0.00} & \num{0.00}\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.01})\\
Age & \num{-0.19}* & \num{-0.20}* & \num{-0.20}* & \num{-0.20}*\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
Human Interaction*Urbanicity &  & \num{-0.14}* &  & \\
 &  & (\num{0.05}) &  & \\
Online-Offline*Urbanicity &  &  & \num{-0.12}* & \\
 &  &  & (\num{0.03}) & \\
Social Media*Urbanicity &  &  &  & \num{-0.13}\\
 &  &  &  & (\num{0.07})\\
\midrule
N & \num{2173} & \num{2173} & \num{2173} & \num{2173}\\
R2 & \num{0.08} & \num{0.08} & \num{0.09} & \num{0.08}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05}\\
\end{tabular}
\begin{tablenotes}
\item \textit{Note: } 
\item Estimates are derived using ordinary least squares
\end{tablenotes}
\end{threeparttable}

\end{table}%

@@

\centering{

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-social-isolation-interactions-1.pdf}

@@

\section{Conclusion}\label{conclusion}

@@

\section{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-ademiluyi2022}
Ademiluyi, A., Li, C., \& Park, A. (2022). Implications and Preventions
of Cyberbullying and Social Exclusion in Social Media: Systematic
Review. \emph{JMIR Formative Research}, \emph{6}(1), e30286.
\url{https://doi.org/10.2196/30286}

\bibitem[\citeproctext]{ref-alabri2022}
Alabri, A. (2022). Fear of Missing Out (FOMO): The Effects of the Need
to Belong, Perceived Centrality, and Fear of Social Exclusion.
\emph{Human Behavior and Emerging Technologies}, \emph{2022}, e4824256.
\url{https://doi.org/10.1155/2022/4824256}

\bibitem[\citeproctext]{ref-alhassan2018}
Alhassan, A. A., Alqadhib, E. M., Taha, N. W., Alahmari, R. A., Salam,
M., \& Almutairi, A. F. (2018). The relationship between addiction to
smartphone usage and depression among adults: a cross sectional study.
\emph{BMC Psychiatry}, \emph{18}(1), 1--8.
\url{https://doi.org/10.1186/s12888-018-1745-4}

\bibitem[\citeproctext]{ref-aljomaa2016}
Aljomaa, S. S., Al.Qudah, M. F., Albursan, I. S., Bakhiet, S. F., \&
Abduljabbar, A. S. (2016). Smartphone addiction among university
students in the light of some variables. \emph{Computers in Human
Behavior}, \emph{61}, 155--164.
\url{https://doi.org/10.1016/j.chb.2016.03.041}

\bibitem[\citeproctext]{ref-al-kandari2021}
Al-Kandari, Y. Y., \& Al-Sejari, M. M. (2021). Social isolation, social
support and their relationship with smartphone addiction.
\emph{Information, Communication \& Society}, \emph{24}(13), 1925--1943.
\url{https://doi.org/10.1080/1369118X.2020.1749698}

\bibitem[\citeproctext]{ref-appel2020}
Appel, M., Marker, C., \& Gnambs, T. (2020). Are Social Media Ruining
Our Lives? A Review of Meta-Analytic Evidence. \emph{Review of General
Psychology}, \emph{24}(1), 60--74.
\url{https://doi.org/10.1177/1089268019880891}

\bibitem[\citeproctext]{ref-beyens2020}
Beyens, I., Pouwels, J. L., Driel, I. I. van, Keijsers, L., \&
Valkenburg, P. M. (2020). The effect of social media on well-being
differs from adolescent to adolescent. \emph{Scientific Reports},
\emph{10}(1), 10763. \url{https://doi.org/10.1038/s41598-020-67727-7}

\bibitem[\citeproctext]{ref-buxfcttner2022}
Büttner, C. M., \& Rudert, S. C. (2022). Why didn't you tag me?!: Social
exclusion from Instagram posts hurts, especially those with a high need
to belong. \emph{Computers in Human Behavior}, \emph{127}, 107062.
\url{https://doi.org/10.1016/j.chb.2021.107062}

\bibitem[\citeproctext]{ref-chen2017}
Chen, C., Zhang, K. Z. K., Gong, X., Zhao, S. J., Lee, M. K. O., \&
Liang, L. (2017). Examining the effects of motives and gender
differences on smartphone addiction. \emph{Computers in Human Behavior},
\emph{75}, 891--902. \url{https://doi.org/10.1016/j.chb.2017.07.002}

\bibitem[\citeproctext]{ref-duradoni2020}
Duradoni, M., Innocenti, F., \& Guazzini, A. (2020). Well-Being and
Social Media: A Systematic Review of Bergen Addiction Scales.
\emph{Future Internet}, \emph{12}(2), 24.
\url{https://doi.org/10.3390/fi12020024}

\bibitem[\citeproctext]{ref-ellison2007}
Ellison, N. B., Steinfield, C., \& Lampe, C. (2007). The Benefits of
Facebook {``}Friends:{''} Social Capital and College Students{'} Use of
Online Social Network Sites. \emph{Journal of Computer-Mediated
Communication}, \emph{12}(4), 1143--1168.
\url{https://doi.org/10.1111/j.1083-6101.2007.00367.x}

\bibitem[\citeproctext]{ref-henning-smith2018}
Henning-Smith, C., Ecklund, A., \& Kozhimannil, K. (2018). RURAL-URBAN
DIFFERENCES IN SOCIAL ISOLATION AND ITS RELATIONSHIP TO HEALTH.
\emph{Innovation in Aging}, \emph{2}(Suppl 1), 770.
\url{https://doi.org/10.1093/geroni/igy023.2851}

\bibitem[\citeproctext]{ref-ivie2020}
Ivie, E. J., Pettitt, A., Moses, L. J., \& Allen, N. B. (2020). A
meta-analysis of the association between adolescent social media use and
depressive symptoms. \emph{Journal of Affective Disorders}, \emph{275},
165--174. \url{https://doi.org/10.1016/j.jad.2020.06.014}

\bibitem[\citeproctext]{ref-jimuxe9nez2022}
Jiménez, A. C., Vaillancourt, M., Zhu, P., \& Seon, Q. (2022). Social
Media and Mental Health: What We Know. \emph{McGill Journal of
Medicine}, \emph{20}(2). \url{https://doi.org/10.26443/mjm.v20i2.852}

\bibitem[\citeproctext]{ref-kaye2017}
Kaye, L. W. (2017). Older adults, rural living, and the escalating risk
of social isolation. \emph{Public Policy \& Aging Report}, \emph{27}(4),
139--144. \url{https://doi.org/10.1093/ppar/prx029}

\bibitem[\citeproctext]{ref-kim2017}
Kim, H. H. (2017). The impact of online social networking on adolescent
psychological well-being (WB): A population-level analysis of korean
school-aged children. \emph{International Journal of Adolescence and
Youth}, \emph{22}(3), 364--376.
\url{https://doi.org/10.1080/02673843.2016.1197135}

\bibitem[\citeproctext]{ref-koning2017}
Koning, J. L. D., Stathi, A., \& Richards, S. (2017). Predictors of
loneliness and different types of social isolation of rural-living older
adults in the United Kingdom. \emph{Ageing \& Society}, \emph{37}(10),
2012--2043. \url{https://doi.org/10.1017/S0144686X16000696}

\bibitem[\citeproctext]{ref-larson2018}
Larson, L. R., Szczytko, R., Bowers, E. P., Stephens, L. E., Stevenson,
K. T., \& Floyd, M. F. (2018). Outdoor Time, Screen Time, and Connection
to Nature: Troubling Trends Among Rural Youth? \emph{Environment and
Behavior}. \url{https://doi.org/10.1177/0013916518806686}

\bibitem[\citeproctext]{ref-nowland2018}
Nowland, R., Necka, E. A., \& Cacioppo, J. T. (2018). Loneliness and
Social Internet Use: Pathways to Reconnection in a Digital World?
\emph{Perspectives on Psychological Science}, \emph{13}(1), 70--87.
\url{https://doi.org/10.1177/1745691617713052}

\bibitem[\citeproctext]{ref-ostic2021}
Ostic, D., Qalati, S. A., Barbosa, B., Shah, S. M. M., Galvan Vela, E.,
Herzallah, A. M., \& Liu, F. (2021). Effects of social media use on
psychological well-being: A mediated model. \emph{Frontiers in
Psychology}, \emph{12}.
\url{https://www.frontiersin.org/articles/10.3389/fpsyg.2021.678766}

>>>>

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Lonely and online: an investigation of social media use and social isolation in China},
  pdfkeywords={Social Isolation, Social Media, Digital
Communication, China},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keywords}
    Social Isolation, Social Media, Digital Communication, 
    China
\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{literature-review-and-theory}{%
\section{Literature Review and
Theory}\label{literature-review-and-theory}}

@@

\hypertarget{data-measurement-and-descriptives}{%
\section{Data, Measurement, and
Descriptives}\label{data-measurement-and-descriptives}}

@@

{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-social-iso-dist-1.pdf}

@@

\end{figure}

@@

{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-var-dist-1.pdf}

@@

{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-sm-use-dist-1.pdf}

@@

{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-urban-dist-1.pdf}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\hypertarget{tbl-profile-models}{}
\begin{table}
\caption{\label{tbl-profile-models}Modeling Profiles of Digital Communication }\tabularnewline

\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
  & Human Interaction & Online/Offline Interaction & General Social Media\\
\midrule
SES & \num{2.35}* & \num{2.16}* & \num{0.24}*\\
 & (\num{0.27}) & (\num{0.28}) & (\num{0.03})\\
Female & \num{-0.03} & \num{-0.35}* & \num{0.01}\\
 & (\num{0.08}) & (\num{0.08}) & (\num{0.01})\\
CCP Member & \num{-0.17} & \num{0.23}* & \num{0.01}\\
 & (\num{0.09}) & (\num{0.09}) & (\num{0.01})\\
Age & \num{0.51}* & \num{-0.82}* & \num{-0.12}*\\
 & (\num{0.26}) & (\num{0.27}) & (\num{0.02})\\
\midrule
N & \num{2277} & \num{2276} & \num{2198}\\
Pseudo R2 & \num{0.07} & \num{0.05} & \\
R2 &  &  & \num{0.05}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.05}\\
\end{tabular}
\begin{tablenotes}
\item \textit{Note: } 
\item Human Interaction and Offline/Online Relationships estimates are derived from ordered logit and General Social Media from ordinary least squares.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\hypertarget{tbl-social-isolation-models}{}
\begin{table}
\caption{\label{tbl-social-isolation-models}Modeling Social Isolation }\tabularnewline

\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
Human Interaction & \num{-0.14}* & \num{-0.04} & \num{-0.14}* & \num{-0.14}*\\
 & (\num{0.02}) & (\num{0.04}) & (\num{0.02}) & (\num{0.02})\\
Online-Offline & \num{0.07}* & \num{0.07}* & \num{0.15}* & \num{0.07}*\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.03}) & (\num{0.01})\\
Social Media & \num{0.05}* & \num{0.05}* & \num{0.05}* & \num{0.13}*\\
 & (\num{0.03}) & (\num{0.02}) & (\num{0.02}) & (\num{0.05})\\
Urbanicity & \num{-0.04}* & \num{0.02} & \num{0.01} & \num{0.04}\\
 & (\num{0.01}) & (\num{0.03}) & (\num{0.02}) & (\num{0.05})\\
SES & \num{-0.04} & \num{-0.04} & \num{-0.04} & \num{-0.04}\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & \vphantom{1} (\num{0.03})\\
Female & \num{0.02}* & \num{0.02}* & \num{0.02}* & \num{0.02}*\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & \vphantom{1} (\num{0.01})\\
CCP Member & \num{0.00} & \num{0.00} & \num{0.00} & \num{0.00}\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.01})\\
Age & \num{-0.19}* & \num{-0.20}* & \num{-0.20}* & \num{-0.20}*\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
Human Interaction*Urbanicity &  & \num{-0.14}* &  & \\
 &  & (\num{0.05}) &  & \\
Online-Offline*Urbanicity &  &  & \num{-0.12}* & \\
 &  &  & (\num{0.03}) & \\
Social Media*Urbanicity &  &  &  & \num{-0.13}\\
 &  &  &  & (\num{0.07})\\
\midrule
N & \num{2173} & \num{2173} & \num{2173} & \num{2173}\\
R2 & \num{0.08} & \num{0.08} & \num{0.09} & \num{0.08}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05}\\
\end{tabular}
\begin{tablenotes}
\item \textit{Note: } 
\item Estimates are derived using ordinary least squares
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-social-isolation-interactions-1.pdf}

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-ademiluyi2022}{}}%
Ademiluyi, A., Li, C., \& Park, A. (2022). Implications and Preventions
of Cyberbullying and Social Exclusion in Social Media: Systematic
Review. \emph{JMIR Formative Research}, \emph{6}(1), e30286.
\url{https://doi.org/10.2196/30286}

\leavevmode\vadjust pre{\hypertarget{ref-alabri2022}{}}%
Alabri, A. (2022). Fear of Missing Out (FOMO): The Effects of the Need
to Belong, Perceived Centrality, and Fear of Social Exclusion.
\emph{Human Behavior and Emerging Technologies}, \emph{2022}, e4824256.
\url{https://doi.org/10.1155/2022/4824256}

\leavevmode\vadjust pre{\hypertarget{ref-alhassan2018}{}}%
Alhassan, A. A., Alqadhib, E. M., Taha, N. W., Alahmari, R. A., Salam,
M., \& Almutairi, A. F. (2018). The relationship between addiction to
smartphone usage and depression among adults: a cross sectional study.
\emph{BMC Psychiatry}, \emph{18}(1), 1--8.
\url{https://doi.org/10.1186/s12888-018-1745-4}

\leavevmode\vadjust pre{\hypertarget{ref-aljomaa2016}{}}%
Aljomaa, S. S., Al.Qudah, M. F., Albursan, I. S., Bakhiet, S. F., \&
Abduljabbar, A. S. (2016). Smartphone addiction among university
students in the light of some variables. \emph{Computers in Human
Behavior}, \emph{61}, 155--164.
\url{https://doi.org/10.1016/j.chb.2016.03.041}

\leavevmode\vadjust pre{\hypertarget{ref-al-kandari2021}{}}%
Al-Kandari, Y. Y., \& Al-Sejari, M. M. (2021). Social isolation, social
support and their relationship with smartphone addiction.
\emph{Information, Communication \& Society}, \emph{24}(13), 1925--1943.
\url{https://doi.org/10.1080/1369118X.2020.1749698}

\leavevmode\vadjust pre{\hypertarget{ref-appel2020}{}}%
Appel, M., Marker, C., \& Gnambs, T. (2020). Are Social Media Ruining
Our Lives? A Review of Meta-Analytic Evidence. \emph{Review of General
Psychology}, \emph{24}(1), 60--74.
\url{https://doi.org/10.1177/1089268019880891}

\leavevmode\vadjust pre{\hypertarget{ref-beyens2020}{}}%
Beyens, I., Pouwels, J. L., Driel, I. I. van, Keijsers, L., \&
Valkenburg, P. M. (2020). The effect of social media on well-being
differs from adolescent to adolescent. \emph{Scientific Reports},
\emph{10}(1), 10763. \url{https://doi.org/10.1038/s41598-020-67727-7}

\leavevmode\vadjust pre{\hypertarget{ref-buxfcttner2022}{}}%
Büttner, C. M., \& Rudert, S. C. (2022). Why didn't you tag me?!: Social
exclusion from Instagram posts hurts, especially those with a high need
to belong. \emph{Computers in Human Behavior}, \emph{127}, 107062.
\url{https://doi.org/10.1016/j.chb.2021.107062}

\leavevmode\vadjust pre{\hypertarget{ref-chen2017}{}}%
Chen, C., Zhang, K. Z. K., Gong, X., Zhao, S. J., Lee, M. K. O., \&
Liang, L. (2017). Examining the effects of motives and gender
differences on smartphone addiction. \emph{Computers in Human Behavior},
\emph{75}, 891--902. \url{https://doi.org/10.1016/j.chb.2017.07.002}

\leavevmode\vadjust pre{\hypertarget{ref-duradoni2020}{}}%
Duradoni, M., Innocenti, F., \& Guazzini, A. (2020). Well-Being and
Social Media: A Systematic Review of Bergen Addiction Scales.
\emph{Future Internet}, \emph{12}(2), 24.
\url{https://doi.org/10.3390/fi12020024}

\leavevmode\vadjust pre{\hypertarget{ref-ellison2007}{}}%
Ellison, N. B., Steinfield, C., \& Lampe, C. (2007). The Benefits of
Facebook {``}Friends:{''} Social Capital and College Students{'} Use of
Online Social Network Sites. \emph{Journal of Computer-Mediated
Communication}, \emph{12}(4), 1143--1168.
\url{https://doi.org/10.1111/j.1083-6101.2007.00367.x}

\leavevmode\vadjust pre{\hypertarget{ref-henning-smith2018}{}}%
Henning-Smith, C., Ecklund, A., \& Kozhimannil, K. (2018). RURAL-URBAN
DIFFERENCES IN SOCIAL ISOLATION AND ITS RELATIONSHIP TO HEALTH.
\emph{Innovation in Aging}, \emph{2}(Suppl 1), 770.
\url{https://doi.org/10.1093/geroni/igy023.2851}

\leavevmode\vadjust pre{\hypertarget{ref-ivie2020}{}}%
Ivie, E. J., Pettitt, A., Moses, L. J., \& Allen, N. B. (2020). A
meta-analysis of the association between adolescent social media use and
depressive symptoms. \emph{Journal of Affective Disorders}, \emph{275},
165--174. \url{https://doi.org/10.1016/j.jad.2020.06.014}

\leavevmode\vadjust pre{\hypertarget{ref-jimuxe9nez2022}{}}%
Jiménez, A. C., Vaillancourt, M., Zhu, P., \& Seon, Q. (2022). Social
Media and Mental Health: What We Know. \emph{McGill Journal of
Medicine}, \emph{20}(2). \url{https://doi.org/10.26443/mjm.v20i2.852}

\leavevmode\vadjust pre{\hypertarget{ref-kaye2017}{}}%
Kaye, L. W. (2017). Older adults, rural living, and the escalating risk
of social isolation. \emph{Public Policy \& Aging Report}, \emph{27}(4),
139--144. \url{https://doi.org/10.1093/ppar/prx029}

\leavevmode\vadjust pre{\hypertarget{ref-kim2017}{}}%
Kim, H. H. (2017). The impact of online social networking on adolescent
psychological well-being (WB): A population-level analysis of korean
school-aged children. \emph{International Journal of Adolescence and
Youth}, \emph{22}(3), 364--376.
\url{https://doi.org/10.1080/02673843.2016.1197135}

\leavevmode\vadjust pre{\hypertarget{ref-koning2017}{}}%
Koning, J. L. D., Stathi, A., \& Richards, S. (2017). Predictors of
loneliness and different types of social isolation of rural-living older
adults in the United Kingdom. \emph{Ageing \& Society}, \emph{37}(10),
2012--2043. \url{https://doi.org/10.1017/S0144686X16000696}

\leavevmode\vadjust pre{\hypertarget{ref-larson2018}{}}%
Larson, L. R., Szczytko, R., Bowers, E. P., Stephens, L. E., Stevenson,
K. T., \& Floyd, M. F. (2018). Outdoor Time, Screen Time, and Connection
to Nature: Troubling Trends Among Rural Youth? \emph{Environment and
Behavior}. \url{https://doi.org/10.1177/0013916518806686}

\leavevmode\vadjust pre{\hypertarget{ref-nowland2018}{}}%
Nowland, R., Necka, E. A., \& Cacioppo, J. T. (2018). Loneliness and
Social Internet Use: Pathways to Reconnection in a Digital World?
\emph{Perspectives on Psychological Science}, \emph{13}(1), 70--87.
\url{https://doi.org/10.1177/1745691617713052}
